### 2021-07-02 rad-icfp-2021/purerad.tex
writing direct D macro
redoing unf figures
minor corrections intro
rewrote notation

@@

@@

TODO: how to get gradient or subpart of the gradient from the previosu term.

TODO: maybe intuition around here

@@

TODO: use the optimisations to be efficient, just on example?

The full list of optimisations can be found on Figure~\ref{fig:optim}.

>>>>

\label{sub:sourcelang}

@@

We introduce several notations which are useful when defining the transformation for reverse-mode.

\input{figures/notation_D}

@@

Given a term $\Gamma\vdash e : \reals$, we can compute its gradient $\grad_\Gamma e$ from a particular instance of 
$\directD{\rho}{\Gamma}{Y}(e)$. First, $\rho, Y$ specifies if we want to compute the whole gradient regarding the variables from $\Gamma$ or a subset of it.
For a subset $\rho\subset \Gamma$, one chooses $Y$ to be the projection function sending a variable 
$x_i:G$ of $\Gamma$ to $x_i$ if it belongs to $\rho$ and to $0_G$ otherwise.
In particular, we take $Y=Id_\Gamma$ to compute the whole gradient.
Next, the gradient will be given by the second part of the pair $\directD{\rho}{\Gamma}{Y}(e)$, 
and we need to initialise the tangent variables. All of them are set to $0$ except the one corresponding to the output value of !e!, 
which we initialise at $1$ to run the backpropagation. 
All in all, we compute the gradient via $\pi_2\directD{\rho}{\Gamma}{Id_\Gamma}(e)(0_\Gamma,1)$.

@@

Though this transformation already has the right complexity, 
its purity allows us to take the most out of generic optimisations.  
A list of common optimisations that are useful for this language can be found in Figure~\ref{fig:optim}.

TODO: use the optimisations to be efficient on example
